Draft

### 2016-07-16 Photosynthesis Course Note.tex
Update light-harvesting notes to the new course. Add notes for Q.F.T.

\section{July 1th}
\label{sec:July_1th}
Begin with a review of two modes of excitons in organic system
\textbf{pp.1}, this
lecture proceeds to explain in detail the dipole interaction potential
(\textbf{pp.2 to 3})
$V_{uv}$ mentioned in previous lecture. \textbf{Page 4} digresses on
the difference between the transition dipole moment and the
permanent dipole moment. The picture shows the transition dipole
moment for a Bacteriacholorophyll (the photosynthetic pigments that 
occur in various phototrophic bacteria). The right side plot illustrates
the absorption spectra for Bacteriacholorophyll.
\textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
strength.

The following slide comes back to the excitation energy. It states two
forms of dimer: the J aggregation ( \textbf{pp.9 to 10}, and the H
aggregation ( \textbf{pp.11}). The accessible energy level for absorption
is determined by conservation of moment. As the result, the J aggregated
dimer absorbs less energy than the monomer case, and a red shift will be
observed when comparing the absorption spectra. The case of H aggregation
is similar. \textbf{Page 12 to 13 } mentions the transition dipole in
more complicated cases. \footnote{Reference could be found in \textit{
J. Phys. Chem. B, Vol. 107, No. 35, 2003}.}

@@

\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

>>>>

\section{July 1th}
\label{sec:July_1th}
Begin with a review of two modes of excitons in organic system
\textbf{pp.1}, this
lecture proceeds to explain in detail the dipole interaction potential
(\textbf{pp.2 to 3})
$V_{uv}$ mentioned in previous lecture. \textbf{Page 4 to 5} digresses on
the difference between the transition dipole moment and the
permanent dipole moment. On page 4, the picture shows the transition dipole
moment for a Bacteriacholorophyll (the photosynthetic pigments that 
occur in various phototrophic bacteria). The right side plot illustrates
the absorption spectra for Bacteriacholorophyll. Page 5 originally
contains an animated display, which is lost in this PDF file, although
the content is not important.
\textbf{Page 6 and 7} also digresses on eletronic momenta and oscillator
strength.

The following slide comes back to the excitation energy. It states two
forms of dimer: the J aggregation (\textbf{pp.9 to 10}), and the H
aggregation (\textbf{pp.11}). The accessible energy level for absorption
is determined by conservation of moment. As the result, the J aggregated
dimer absorbs less energy than the monomer case, and a red shift will be
observed when comparing the absorption spectra. The case of H aggregation
is similar. \textbf{Page 12 to 13 } mentions the transition dipole in
more complicated cases. \footnote{Reference could be found in \textit{
J. Phys. Chem. B, Vol. 107, No. 35, 2003}.}

@@

\section{July 13th}
\label{sec:July_13th}

In this lecture, we start with a review of simple harmonic
oscillators in quantum mechanics (\textbf{pp.1 to 8}).
Then turn to the introduction of Glauber coherent states.

\paragraph{Glauber Coherent States} (defined on \textbf{pp.9})
is the eigenstate of the annilation 
operator:
    \begin{align}
        A \ket{\alpha} = a \ket{\alpha}
    \end{align}
These states maintain their coherence usually longer those number
eigenstates. There are other features of the Glauber coherent state,
mentioned in \textbf{pp.9 to 10}.

The next few deductions will give us a very physical picture of Glauber
coherent states. First, express Glauber coherent state as a linear
combination of number eigenstates (\textbf{pp.11 to 14}). 
(It is also found that different coherent states are note 
orthogonal (\textbf{pp.15}). Also, the overlap of
two coherent state decays expoentially as the difference 
of the eigenvalues $|\alpha-\beta|$.

\textbf{Digression}: usualy, the coherent state representation is
much more numerical efficient in computer simulation
than the number representation.

Next, we explore several interesting properties of these coherent
states:
\begin{itemize}
    \item \textbf{Expectations}
        (\textbf{pp.16 to 17}) It is found that 
        $\braket{X}=\sqrt{2}\lambda \text{Re}(\alpha)$,
        and $\braket{P} = \frac{\sqrt{2}\hbar}{\lambda} \text{Im}(\alpha)$. Or:
        $\alpha$ is related to $\braket{\alpha|X|\alpha}$
        and $\braket{\alpha|P|\alpha}$. Hence a real $\alpha$ means the state
        $\ket{\alpha}$ is a static state with $\braket{P}=0$. Moreover, this 
        state
        is the lowest energy eigenstate of a simple harmonic oscillator with
        the origin shifted from $0$ to $\alpha$. 
        % todo substantiate this point!
    \item \textbf{Variance}
        (\textbf{pp.18 to 20})
        It is also found that the variance 
        $(\Delta X)^2 = \frac{\lambda^2}{2}$,
        this is exactly the same as the variance of the gound state of simple
        harmonic oscillator.
        And $(\Delta P)^2 = \frac{\hbar^2}{2\lambda^2}$. 
        From the two expression,
        we see that any coherent states have the same minimal uncertainty:
        $\Delta X \cdot \Delta P = \frac{\hbar}{2}$.
    \item \textbf{Time Evolution}
        (\textbf{pp.21})
        Using the energy eigenstate of simple harmonic oscillator, we can find 
        the time evolution of coherent state as 
        $\alpha(t) = e^{-i\omega t} \alpha_0$. It shows that $\alpha$ is really
        like a \textit{classical oscillator} and the norm $|\alpha|^2$ is conserved. 
        This is so cool!
\end{itemize}

The next slide (\textbf{pp.22}) summarizes the classical feature of Glauber coherent state.

Then we turn to its application in biophysics.
\paragraph{Polaron dynamics in LH1/LH2} We first introduces polaron
(\textbf{pp.24 to 25}). The \textbf{polaron model}: Polaron
is short for polarized electron. In a polarized crystal, an moving electron
will deform the lattice. Then polaron is the electron and those deformed
part put it together. This seems quite like the copper pair picture in
BCS theory. In the light-harvesting system, since only a very small
amount of light is captured, the exciton concentration is low. And we can
use the polaron picture for electrons.

Next we write out the Hamiltonian for the LH1/2. (\textbf{pp.26})
The phonon $H_{ph}$ term 
contains 16 phonons for 16 pigments in LH1. The exciton term $H_{ex}$
assumes that the interaction is only nearst neighbour interaction.
The exciton-phonon interaction $H_{\text{ex-ph}}$ is essentially
the usual electron-phonon interaction term in solid state physics.
\section{July 15}
\label{sec:July_15}

% $q$ represent the phonon vibration. Since $\Omega(Q) = \Omega(0) = 
% \frac{\partial}{\partial q}q + ...$, the linear-diagonal coupling
% is just the first.
% $\gamma_{mn}^l$, $\gamma_0$ is the energy for the phonon on the same
% site. 
Here we first introduces a new term in the Hamiltonian, 
$H_{\text{ex-ph}}^{\text{off-diagonal}}$.

Taking a linear approximation of the phonon band. We will find
a Hunag-Rhys factor $S$ in $\sum_q g_q^2 \omega_q = S\omega_0$.

We will use a time-dependent variational calculation. Then
we introduces a Davydov ansatz. Note that
\begin{align*}
    e^{A+B} = e^A e^B e^{\frac{1}{2}[A,B]}
\end{align*}
% todo check this
And using this relationship, it could be found that the $\ket{\beta}$
is actually a Glauber coherent state.

note that the Davydov ansatz is not translational invariant.

Next we project the Davydov ansatz into bloch states, and get
the Toyozawa's ansatz. This Toyozawa ansatz has a central
position. Using thise, we get the energy band.

Explain for the energy band.
% todo level repulsion

Shows a Holstein polaron's phase diagram. Outside the thin region,
there is always a unique solution (global minimum for the variational
parameters). Below the region, large polaron. Above, small polaron.
% todo what is a large polaron.
Inside the solid region, there will be two solutions coexisting.
The the solution obatined depeands on the initial configuration.
The physical picture is that, changing the value of $J$ and $g$,
the size of polaron will change sharply when one transverse the
dashed line.

Shows some variational parameters calculated. The strange wedge
in the picture, is the mode of $q=0$ mode ($\beta_{q=0} = g$). It is
called the Goldston mode, decoupled from the system. This explains
that the constant value inside these plots, when $q=0$.

When we calculate the off-diagonal coupling. There will be two
wedges

Then freqency plot. The labels are $(J,g,\phi)$, where $\phi$
is the off-diagonal strength.

Another approach, called the Munn-Silbey Method,
in which one first do a strange transformation
and 
\section{License}
The entire content of this work (including the source code
for TeX files and the generated PDF documents) by 
Hongxiang Chen (nicknamed we.taper, or just Taper) is
licensed under a 
\href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative 
Commons Attribution-NonCommercial-ShareAlike 4.0 International 
License}. Permissions beyond the scope of this 
license may be available at \url{mailto:we.taper[at]gmail[dot]com}.

### 2016-07-16 draft.tex
Update light-harvesting system (Photosynthesis) notes.
Update light-harvesting notes to the new course. Add notes for Q.F.T.

    \subsection{By Mingyuan Hunag}
    Too boring.

@@

\section{Problems in Bernevig's Topological ...}

@@

    \begin{align}
        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
            (\eta_b,U_{ac}\dot{\psi}_c
    \end{align}
    \subsection{Quantum Statistical Mechanics}
    \label{sec:Quantum Statistical Mechanics}
    \begin{defi}[Time Evolution Operator]
        The time evolution operator $U(t,t_0)$ is defined such that
        \begin{align}
            \label{eq:def_time_evo_op}
            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
        \end{align}
    \end{defi}
    It satisfy the relationship:
    \begin{align}
        \label{eq:def_time_evo_op 2}
        i\hbar \partial_t U(t,t_0)= \mathcal{H} U(t,t_0)
    \end{align}
    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
    Equations.

@@

    Density matrix satisfies several good properties:
    \begin{itemize}
        \item Normalized
        \item Hermiticity
        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
    \end{itemize}
    \subsection{The Mathematical Theory of Communication}
    \label{sec:The_Mathematical_Theory_of_Communication}
    \subsubsection{Introduction}

@@

\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.

>>>>

    \subsection{By Mingyuan Hunag}
    Not insterested.

@@

    \subsection{By Liyuan Zhang}
    Not insterested.
\section{Problems in Bernevig's Topological ...}

@@

    \begin{align}
        0=(\eta_b,\dot{\eta_a}) = (\eta_b,\dot{U}_{ac}\psi) +
            (\eta_b,U_{ac}\dot{\psi}_c
    \end{align}
    \subsection{Quantum Statistical Mechanics}
    \label{sec:Quantum Statistical Mechanics}
    \begin{defi}[Time Evolution Operator]
        The time evolution operator $U(t,t_0)$ is defined such that
        \begin{align}
            \label{eq:def_time_evo_op}
            \ket{\Psi(t)} = U(t,t_0) \ket{\Psi(t_0)}
        \end{align}
    \end{defi}
    It satisfy the relationship:
    \begin{align}
        \label{eq:def_time_evo_op 2}
        i\hbar \partial_t U(t,t_0)= H U(t,t_0)
    \end{align}
    This is obvious when substituting $U(t,t_0)$ into the Schrodinger 
    Equations.

@@

    Density matrix satisfies several good properties:
    \begin{itemize}
        \item Normalized
        \item Hermiticity
        \item Positivity. For any $\Phi$, $\braket{\Phi|\rho|\Phi} \geq 0$.
    \end{itemize}
    The time evolution of density matrix, directly obtained from Schrodinger's
    equation, is
    \begin{align}
        \label{eq:quantum_macrostates:density_matrix:evolution}
        i\hbar \frac{\partial}{\partial t}\rho = [H,\rho]
    \end{align}

    \subsection{The Mathematical Theory of Communication}
    \label{sec:The_Mathematical_Theory_of_Communication}
    \subsubsection{Introduction}

@@

\section{Quantum Field Theory}
\label{sec:Quantum_Field_Theory}
    \subsection{Relatvistic Quantum Mechanics}
    \label{sec:Relatvistic_Quantum_Mechanics}

    \subsubsection{2.1 Quantum Mechanics}
    \label{sec:2.1_Quantum_Mechanics}
    This part sumarize the axioms of quantum mechanics. (Omitted)
    However, one class of important but seldom mentioned operator,
    the antilinear operators and the antiunitary operators are not
    discussed here but postponed to the next part.

    \subsubsection{2.2 Symmetries}
    \label{sec:2.2_Symmetries}
    This part discribe some important theorems concerning the symmetries
    in quantum mechanics.

    Firstly, symmetries in quantum mechanics some times requires the use
    of antilinear and antiunitary operators.

    \paragraph{Antilinear and Antiunitary}
    Antilinear operators: $U (\lambda A + \upsilon B)
                            = \lambda^* UA + \upsilon^* UB$.

    Antiunitary: $ (U \phi, U \psi) = (\psi, \phi) = (\phi,\psi)^*$

    The adjoint operator of an antilinear operator requires special
    attention:
    $$ (\phi, A^\dagger\psi) = (A\phi, \psi)^*$$
    (The usual definition will become troublesome since the LHS will
    be antilinear in $\phi$, whereas the RHS is linear.)

    Thankfully, the criterion for unitarity or antiunitarity is the same:
    $$U^\dagger = U^{-1}$$

    An important example is those symmetries which can be infinitesimally
    close to identity. In the vincinity of unity, it is:
    $$ U =1+i\epsilon t $$
    where $t$ is Hermitian and linear.
    % TODO why is it Hermitian?

    \paragraph{Symmetry Group and its Representation} The set of all
    symmetries transformations obviously can have a group structure.
    By giving each symmetry transformation a unitary or antiunitary
    operator, a representation of such group is obtained. However,
    such a representation can be projective (projective as in
    projective geometry, or $\mathbb{CP}^n$), since operators acts
    on ket spaces, which is already projective (within a freedom of
    phase).

    If the phase is taken into consideration, it is found that this
    phase is independent of the ket that the operator acts on:
    \begin{align}
        \label{eq:2.2_symmetries_projective_phase}
        U(T_1 T_2) \Psi = e^{i\phi} U(T_1) U(T_2) \Psi
    \end{align}
    Here $U(T_1)$/$U(T_2)$ is the operator corresponding to the symmetry
    transformation $T_1$/$T_2$. $\phi$ is the phase, depends only
    on $T_1 T_2$.

    Howver, there is one exception to this rule. It exists when the
    state $\Psi$ is not the linear some of some other wave functions.
    That is, we can not express $\Psi$ as $\sum_i \lambda_i \psi_i$.
    This seems incomprehesible to me.
    % TODO Understand this!
    There are some link on page 53
    between the structure of Lie group associated
    with this symmetry and whether the representation can be projective.
    \footnote{Though not state, it can be infered that a representation
    can be made not-projective by a good choice of $U(T)$, so that
    $\phi \equiv 0$ in \fref{eq:2.2_symmetries_projective_phase} }

    \paragraph{Connected Lie group} is of special importance in physics.
    However, the books description obfuscate the mathematical description
    of this structure. I will update this note later to remedy such
    % TODO update this part.
    discussion. The message I understand is that the representation is
    tightly bound to the Lie algebra. An important example is that when
    $$ U(T(\theta)) \approx 1 + i \theta^a t_a $$
    $$ [t_b,t_c] = 0$$
    then
    $$ U(T(\theta)) = \exp(it_a \theta^a) $$

    \subsubsection{2.3 Quantum Lorentz Transformations}
    \label{sec:2.3_Quantum_Lorentz_Transformations}
    \textbf{Note}: although the title suggests "quantum", this part is
    mostly classical.

    Starting with the invariance of interval:
    \begin{align}
        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval}
        \eta_{\mu\nu}dx'^\mu dx'^\nu = \eta_{\mu\nu}dx^\mu dx^\nu
    \end{align}
    or equivalently % TODO why equivalently?
    \begin{align}
        \label{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
        \eta_{\mu\nu} \frac{\partial x'^\mu}{\partial x^\rho}
            \frac{\partial x'^\nu}{\partial x^\sigma}
            =
        \eta_{\rho\sigma}
    \end{align}
    It claims that any coordinate transformation satisfying 
    \ref{eq:2.3_Quantum_Lorentz_Transformations invariance_of_interval 2}
    must be linear.

    Such linear Lorentz transformations satisfy:
    \begin{align}
        T(\bar{\Lambda},\bar{a})T(\Lambda,a) = 
            T(\bar{\Lambda}\Lambda, \bar{\Lambda}a+\bar{a})
    \end{align}
    where $\bar{\Lambda}+\bar{a}$ and $\Lambda+a$ are two such 
    transformations.

    The $\Lambda$ and $\Lambda^{-1}$ can be determined by several 
    equations that relate it with $\eta_{\mu\nu}$. Note that:
    $$ \Lambda^{\rho}_{ \nu} \neq \Lambda^{ \rho}_\nu$$
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} Bosonization and Strongly Correlated Systems. Cambridge.
